---
title: "viz_ggplot1"
output: github_document
date: "2022-09-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Let's import Data

```{r}
library(tidyverse)
library(ggridges)
```

This codes from the course get data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's make a scatterplot

```{r}
weather_df %>% 
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Let's keep making the same plot but different

```{r}
weather_df %>% 
  drop_na() %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax))+
  geom_point()
```

Let's keep making the same plot but different

```{r}
weather_scatterplot = 
  weather_df %>% 
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax)) 

weather_scatterplot +
  geom_point()
```

## Let's fancy this up a bit

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth()
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE)
```

Make separate panels.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
  ## facet_grid (~ name .)
```

`tmax` and `tmin` are boring, let's spice it up more!

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust = 1))
```

LC: Write a code chain that starts with weather_df; focuses only on Central Park, converts temperatures to Fahrenheit, makes a scatterplot of min vs. max temperature, and overlays a linear regression line (using options in geom_smooth()).


## Some quick stuff
## weather_df %>% 
## mutate (CONVERT TO Fahrenheit)


```{r}
weather_df %>% 
  ggplot (aes(x = tmin, y = tmax)) +
  geom_hex()
```

## Univariate plots ...

Histograms, density, boxplots, violins, ...

```{r}
weather_df %>% 
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

Let's see more options
```{r}
weather_df %>% 
  ggplot(aes(x = tmax, fill = name)) +
  geom_density(alpha = .3) 
```

Boxplots??

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax, fill = name)) +
  geom_boxplot()
```

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax, fill = name)) +
  geom_violin()
```

OR

```{r}
weather_df %>% 
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```

## Saving and embedding plots

First, let's save a plot

```{r}
weather_scatterplot =
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth(sd = FALSE) +
  facet_grid(. ~ name)

weather_scatterplot

ggsave("./results/weather_scatterplot.pdf", weather_scatterplot, width = 8, height = 5)
```

What about embedding?

```{r fig.width = 6, fig.height = 3}
weather_scatterplot
```

Embed at a different size
```{r fig.width = 12, fig.height = 6}
weather_scatterplot
```






